---
output: github_document
always_allow_html: yes
---


<!--
Copyright 2018 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
-->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# drake-example

<!-- badges: start -->
<a id="devex-badge" rel="Inspiration" href="https://github.com/BCDevExchange/assets/blob/master/README.md"><img alt="An idea being explored and shaped. Open for discussion, but may never go anywhere." style="border-width:0" src="https://assets.bcdevexchange.org/images/badges/inspiration.svg" title="An idea being explored and shaped. Open for discussion, but may never go anywhere." /></a>
[![License](https://img.shields.io/badge/License-Apache%202.0-blue.svg)](https://opensource.org/licenses/Apache-2.0)
<!-- badges: end -->

The goal of drake-example is to provide a repo for developing a demo or lesson for using the [drake](https://ropensci.github.io/drake/) package for [R](https://www.r-project.org/) workflows. 

A simple drake workflow:

(1) First --- generate some data:
```{r}
library(here)
source(here("generate_cohort_example.R"))
```

(2) Source the respective `.R` files which define the drake workflow:
```{r setup-drake}
source(here("R/packages.R"))
source(here("R/functions.R"))       
source(here("R/plan.R"))    
```

(3) Run the plan & visualize progress:
```{r}
plan

config <- drake_config(plan)

make(plan)

vis_drake_graph(config)
```

All 3 steps above would typically be contained within a `make.R` file.


### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/drake-example/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.


### License

Copyright 2019 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the "License");
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an "AS IS" BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
