---
output: github_document
always_allow_html: yes
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

This a repo that is a home for developing a lesson and talk around drake based workflows. 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# drake-example

<!-- badges: start -->
<a id="devex-badge" rel="Inspiration" href="https://github.com/BCDevExchange/assets/blob/master/README.md"><img alt="An idea being explored and shaped. Open for discussion, but may never go anywhere." style="border-width:0" src="https://assets.bcdevexchange.org/images/badges/inspiration.svg" title="An idea being explored and shaped. Open for discussion, but may never go anywhere." /></a>
<!-- badges: end -->

The goal of drake-example is to provide a repo for developing a lesson or lecture surrounding drake based workflows. 

The simple drake workflow outlined at the moment first involves generating some data:
```{r}
library(here)
source(here("generate_cohort_example.R"))
```

Then we need to source our respective `.R` files which define the drake workflow:
```{r setup-drake}
source(here("R/packages.R"))
source(here("R/functions.R"))       
source(here("R/plan.R"))    
```

Then lastly we need to run the plan and visualize our progress. This typically would all be contained within a `make.R` file:
```{r}
plan


config <- drake_config(plan)
vis_drake_graph(config)


make(plan)

vis_drake_graph(config)
```


